Which spherical CNN should you use?\\ DeepSphere V2

### 2019-09-10 main.tex
Updates from Overleaf

%\title{Which spherical CNN should you use?\\ DeepSphere V2}
\title{DeepSphere: an efficient graph-based spherical CNN}
%\title{DeepSphere, an efficient (& equivariant) graph-based spherical CNN}

@@

\begin{table}[!ht]
\begin{tabular}{l|c c c c}
        \multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5} 
        \multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} & 94.67 & - & - & -\\
        \cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & 97.5 & 68.6 & - & -\\
        \cite{cohen_gauge_2019} (R2R) & 97.7 & 75.9 & - & -\\ \hline
        % unknown
        DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 ms & 25h \\
        DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 30 ms & 13h\\
        % 12'926'432
    \end{tabular}
    \caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang_spherical_2019}}
\end{table}

@@

batch size 32, adam optimizer, constant learning rate of $5 \cdot 10^{-2}$
cross-entropy loss, and add triplet loss from ``Esteves et al.''

@@

concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
\subsubsection*{Equiangular}
Equiangular sampling, with a latitude bandwidth 384 and longitude bandwidth 576.

@@

\begin{dmath}
    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, GAP\, +\, FCN
\end{dmath}

\end{document}

>>>>

\title{Which spherical CNN should you use?\\ DeepSphere V2}

@@

\begin{table}[!ht]
\begin{tabular}{l|c c c c}
        \multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5} 
        \multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} & 94.67 & - & - & -\\
        \cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & 97.5 & 68.6 & - & -\\
        \cite{cohen_gauge_2019} (R2R) & 97.7 & 75.9 & - & -\\ \hline
        % unknown
        DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 & 25h \\
        DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 30 & 13h\\
        % 12'926'432
    \end{tabular}
    \caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang_spherical_2019}}
\end{table}

@@

batch size 32, adam optimizer, constant learning rate of $5 \cdot 10^{-2}$
cross-entropy loss, and add triplet loss from ``Esteves et al.´´

@@

concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.´´
\subsubsection*{Equiangular}
Equiangular sampling, with a latitude bandwidth 384 and longitude bandwidth 576.

@@

\begin{dmath}
    [GC_{50}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, [GC_{100}\, +\, BN\, +\, ReLU]\, +\, GAP\, +\, FCN
\end{dmath}
\end{document}
